---
headless: true
output: 
  html_document:
    keep_md: true
    preserve_yaml: true
---

```{r knitrrrr, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
```

```{r chart, include=FALSE}
updated <- format(Sys.time(), "%m-%d-%Y (at %H:%M)")
n <- length(list.files(pub.en))
```

# About

This website serves as an archive for scientific publications at 
Inland Norway University of Applied Sciences 
(registered in Cristin since the institution was established on January 1, 2017). 
It is updated monthly.

The archive was last updated **`r updated`** and contains **`r n`** publications.

Use [the archive](#archive) to find publications for faculties and departments 
at the university for a specific year or month. You can also use the search 
function to find individual publications by using, for example, the author's 
name or title.

The estimation of the 17 Sustainable Development Goals (SDGs) outlined in 
Agenda 2030 is based on available abstracts from publications and is calculated
using Bidirectional Encoder Representations from Transformers 
([BERT](https://en.wikipedia.org/wiki/BERT_(language_model))). The models are 
developed by Vanderfeesten et al. 
([2022](https://doi.org/10.5281/zenodo.6487606)) and can be downloaded from 
Jaworek ([2022](https://doi.org/10.5281/zenodo.5835849)).

You may also visit the 
[Zotero library](https://www.zotero.org/groups/5022929/hinn/library).